Contextuality and the Born rule in fuzzy quantum theories

### 2017-05-03 prop_letter.tex
prop_letter.tex \setcounter{secnumdepth}{3} Added...
prop_letter.tex \paragraph{Quantum and Classical IVPMs} Updating...

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
\allowdisplaybreaks
\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
\newcommand{\mul}{\ensuremath{\mu^{\mathrm{L}}}}
\newcommand{\mur}{\ensuremath{\mu^{\mathrm{R}}}}

@@

Quantum IVPMs turns into the classical IVPMs setup~\cite{JamisonLodwick2004}
when the space of events includes only mutually commuting sub-events,
where $\events'\subseteq\events$ is called a sub-event space if it
satisfies the following conditions.
\begin{itemize}
\item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
\end{itemize}
For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\end{equation}
If we identify the density matrices~$\proj{0}$ and $\proj{1}$ as
the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
represents experimenter know nothing about a coin before she tosses
it, and two classical states~$\proj{0}$ and $\proj{1}$ are both
consistent with $\bar{\mu}_{2}$ on $\events_{0}$.

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
\allowdisplaybreaks
\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
\setcounter{secnumdepth}{3}

@@

Quantum IVPMs become classical IVPMs~\cite{JamisonLodwick2004} when
the space of events includes only mutually commuting sub-events, where
$\events'\subseteq\events$ is called a sub-event space if it satisfies
the following conditions.
\begin{itemize}
\item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
\end{itemize}
For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\end{equation}
If we identify the density matrices~$\proj{0}$ and $\proj{1}$ as
the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
represents experimenter know nothing about a coin before she tosses
it, and two classical states~$\proj{0}$ and $\proj{1}$ are both
consistent with $\bar{\mu}_{2}$ on $\events_{0}$.
